### 2015-12-09 paper/4-performance.tex
Rewrote introduction to sequential simulation

\subsection{Sequential Simulation}
%TODO we start with sequential simulation results, because this is still base case
%TODO compare CPU time with adevs for some benchmarks
%TODO and explain why there is such a difference
%TODO (spend some time here, as this is also important)
In our benchmarks, we will consistently compare the performance of dxex with adevs. The implemented models for the each benchmark are functionally identical.\\
Dxex uses integer timestamps whereas adevs uses floating point time representation. Tests show there is little difference performance-wise (both types fit in a machine word).\\
The benchmarks have been compiled using the {\tt -O3} option and link-time optimization, with all IO disabled. To compare the models in details, we have run the different benchmarks with different parameters.\\
The benchmarks have been run on a i7-2670QM, 16GiB RAM, Arch Linux (4.2.5 kernel) and G++ 5.2. Interpretation of the benchmark results is done using call-graphs generated by perf. A selection of those call-graphs is available in the code repository. For the runtime plots, perf is used in combination with R.\\
%Note that a fixed timeadvance (e.g. devstone) is set at 100.
\subsubsection{Devstone}
The Devstone \cite{DEVStone} benchmark is highly hierarchical. As can be seen in Figure~\ref{fig:Devstone}, dxex is outperforming adevs considerably. This can be explained by the fact that, using Direct connection, the hierharchical structure is being flattened whereas, in the adevs case, considerable overhead is caused by traversing the coupled model's structure to pass events.
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig1.eps}
	\caption{Devstone}
	\label{fig:Devstone}
\end{figure}

>>>>

\subsection{Benchmarks}
%TODO

\subsection{Sequential Simulation}
Despite our core contribution being mainly in the parallel simulation, we still value a comprehensive comparison of sequential simulation results.
First, and foremost, as parallel simulation results are tightly linked to the sequential simulation results: parallel simulation merely adds a synchronization layer over different, essentially sequential, simulation kernels.
Second, since parallel simulation results are validated through the use of adevs.
To provide a more comprehensive comparison to adevs in the parallel simulation benchmarks, sequential simulation results need to be compared.

Benchmarks have been run on an \textit{Intel i7-2670QM} with \textit{16GB of main memory} on Linux.
Results were obtained through the use of \textit{perf}.
A selection of call-graphs and more detailed results can be found online.

%Note that a fixed timeadvance (e.g. devstone) is set at 100.
\subsubsection{Devstone}
The Devstone \cite{DEVStone} benchmark is highly hierarchical. As can be seen in Figure~\ref{fig:Devstone}, dxex is outperforming adevs considerably. This can be explained by the fact that, using Direct connection, the hierharchical structure is being flattened whereas, in the adevs case, considerable overhead is caused by traversing the coupled model's structure to pass events.
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig1.eps}
	\caption{Devstone}
	\label{fig:Devstone}
\end{figure}
